\addcontentsline{toc}{chapter}{\protect Acknowledgments}


\chapter*{Acknowledgments}
\noindent
The last ten month have been a great time for me. Both challenging and exhausting but great and exciting. In my opinion we should soften the distinction between the different departments even further. Interdisciplinarity becomes more and more important as the complexity of modern research increases. Computational physics requires good software engineering. Likewise, Software Engineers can benefit from the knowledge of physicists or mathematicians. This is the reason why I liked the idea of writing a simulation framework so much. Although it's not a common thing to do in a physics master thesis, I learned a lot about programming. I really want to thank you - Prof. Ruhl - for sharing this opinion with me and for giving me the opportunity to write this thesis and of course for your input all along the way. It was always fun and inspiring to discuss with you about physics and non-physics related topics like climate change, electro mobility and the education system, just to mention a few. \\
\newline
Especially the last three month have been hard, because I already started my regular job in April. Thanks for your understanding and support!\\
\newline
Also big thanks to Ute Tobiasch for your reliability and scheduling all the appointments.\\
\newline
Thanks to my friends Horos Cuesdeanu, Alexander-Cornelius Heinrich and Manuel \\
Salzberger for proofreading.\\
\newline
Finally I want to thank my colleagues Julian Manke and Manuel Linder whom I shared an office with. Thanks for your support, the long discussions and your help! \\


